tstrait: a quantitative trait simulator for ancestral recombination graphs

### 2023-11-28 paper.tex
Use journal abbreviations
Tweak abstract

\abstract{
\textbf{Summary:}
Ancestral recombination graphs (ARGs) encode the ensemble of correlated
genealogical trees arising from recombination in a compact and efficient
structure, and are of fundamental importance in population and statistical
genetics. Recent breakthroughs have made it possible to simulate and
infer ARGs at the population scale, and there is now intense interest
in applying ARG-based methods across a broad range of applications.
Genome-wide association studies (GWAS) are one of the most important
application areas, with ARG-based methods already providing substantial
improvements over the state-of-the-art.
Sophisticated methods exist to simulate ARGs based on a variety
of population genetic models, but there is currently no method
to simulate quantitative traits directly from these ARGs.
To apply existing quantitative trait simulators users must export
genotype data, losing important information about ancestral processes
and producing large files when applied
to Biobank-scale datasets.
We present \texttt{tstrait},
an open-source Python library to simulate
quantitative traits on ARGs, and show how this user-friendly software
can quickly simulate phenotypes for Biobank-scale datasets
on a laptop computer.
\\\textbf{Availability and Implementation:} \texttt{tstrait} is available
for download on the Python Package Index.
Full documentation with examples and workflow
templates is available on \url{https://tskit.dev/tstrait/docs/}, and the
development version is maintained on Github
(\url{https://github.com/tskit-dev/tstrait}).\\ \textbf{Contact:}
\href{daiki.tagami@hertford.ox.ac.uk}{daiki.tagami@hertford.ox.ac.uk}\\
}

>>>>

\abstract{
\textbf{Summary:}
Ancestral recombination graphs (ARGs) encode the ensemble of correlated
genealogical trees arising from recombination in a compact and efficient
structure, and are of fundamental importance in population and statistical
genetics. Recent breakthroughs have made it possible to simulate and
infer ARGs at biobank scale, and there is now intense interest
in using ARG-based methods across a broad range of applications,
particularly in genome-wide association studies (GWAS).
Sophisticated methods exist to simulate ARGs using
population genetics models, but there is currently no software
to simulate quantitative traits directly from these ARGs.
To apply existing quantitative trait simulators users must export
genotype data, losing important information about ancestral processes
and producing prohibitively large files when applied
to the biobank-scale datasets currently of interest in GWAS.
We present \texttt{tstrait},
an open-source Python library to simulate
quantitative traits on ARGs, and show how this user-friendly software
can quickly simulate phenotypes for biobank-scale datasets
on a laptop computer.
\\\textbf{Availability and Implementation:} \texttt{tstrait} is available
for download on the Python Package Index.
Full documentation with examples and workflow
templates is available on \url{https://tskit.dev/tstrait/docs/}, and the
development version is maintained on GitHub
(\url{https://github.com/tskit-dev/tstrait}).\\ \textbf{Contact:}
\href{daiki.tagami@hertford.ox.ac.uk}{daiki.tagami@hertford.ox.ac.uk}\\
}
